Synthesizing Symmetric Lenses

### 2019-02-28 papers/SymmetricLenses/main.tex
add fixes and keep 25 pages

\newif\ifdraft\drafttrue  % set true to show comments
% \newif\ifdraft\draftfalse  % set true to show comments
\newif\ifanon\anontrue    % set true to suppress names, etc.
\newif\ifappendices\appendicesfalse

@@

Each task consists of a source and target regular expression and a set of
examples. These tasks can be quite quite large, as we are synthesizing complex
transformations between real file formats -- some of the lenses and
specifications are over 500 AST nodes \afm{run the experiments and collect the
  data at some point}.

>>>>

\newif\ifdraft\draftfalse  % set true to show comments
% \newif\ifdraft\draftfalse  % set true to show comments
\newif\ifanon\anontrue    % set true to suppress names, etc.
\newif\ifappendices\appendicesfalse

@@

Each task consists of a source and target regular expression and a set of
examples. We are synthesizing transformations between real formats, so these
tasks are can be quite large -- on average, the size of each RE
in the specification is 1637 and the size of the synthesized lens is 3254.
